### 2020-02-28 ChapterBackground/chapterBackground.tex
Updated: Basic description of collision response

\subsection{Collision Detection}\label{collision_detection}
Objects are represented by geometry colliders. Collision detection works by detecting overlaps between geometry representations.
Typically objects have simple colliders, such as boxes, capsules, cylinders and spheres. More complex colliders are often supported, such as convex and concave hulls. Colliders can either be static or dynamic.

@@

@@

%\subsection{Constraints}

>>>>

\subsection{Collision Detection}\label{collision_detection}
Objects are represented by geometry colliders. Collision detection works by detecting overlaps between geometry representations  (contact determination).
Typically objects have simple colliders, such as boxes, capsules, cylinders and spheres. More complex colliders are often supported, such as convex and concave hulls. Colliders can either be static or dynamic.

@@

In addition to informing the collision response phase, callbacks can also be generated, allowing any part of the software to be informed of collision events that have taken place. For example, the game logic may receive events of when a bullet hits an avatar in order to determine when a player has been shot in a shooting game.

@@

Collision response is the phase of the real-time physics loop which deals with integrating into the model the effect produced by contacts between entities within the system. Collision response will taken into account mass, coefficient of restitution (loss of kinetic energy during a collisions) and the location and angle of the collision. Collision response can be very simple to calculate for simple geometric shapes, but becomes expensive when more complex mesh representations are used.
%\subsection{Constraints}
